学術論文

### 2021-08-05 articles.Rmd
update

- [33] Shimono, Y., Hasegawa, A., Tsuchihara, K., Tanaka, K., Matsuda, Y., & Kunisato, Y.(in press) Longitudinal association between autistic traits and affinity for hikikomori in Japanese university students. Current Psychology,

>>>>

- [35] Hasegawa, A., Somatori, K., Nishimura, H., Hattori, Y., & Kunisato, Y. (in press). Depression, rumination, and impulsive action: A latent variable approach to behavioral impulsivity. The Journal of Psychology.

- [34] Wang K., Goldenberg A., Dorison, C.A., Miller, J.K., Uusberg, A., Lerner, J.S., Gross, J.J., Agesin, B.B., Bernardo, M., Campos, O., Eudave, L., Grzech, K., Ozery, D.H., Jackson, E.A., Luis Garcia, E.O., Drexler, S.M., Jurković, A.P., Rana, K., Wilson, J.P., ... Kunisato, Y.,...Moshontz, H. (in press) A multi-country test of brief reappraisal interventions on emotions during the COVID-19 pandemic. Nature Human Behavior https://doi.org/10.1038/s41562-021-01173-x
